BERT Model Compression and Weight Sharing

### 2019-05-12 paper/paper.tex
Add tentative abstract bullet points

\begin{abstract}
  \begin{itemize}
  \item This document describes the expected style, structure, and rough
  proportions for your final project write-up.
  \item While you are free to break from this structure, consider it a strong
  prior for our expectations of the final report.
  \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
  in this format. While you can include supplementary material, it will not be
  factored into the grading process. It is your responsibility to convey the
  main contributions of the work in the length given.
  \end{itemize}

>>>>

\begin{abstract}
\raggedright
  \begin{itemize}
  \item We apply model compression results to fine-tuned BERT on multiclass
  classification problems.
  \item Knowledge distillation and DeepTwist-based compression techniques give
  us moderate compression benefits for a commensurate decrease in model
  performance.
  \item We achieve our most compelling results from employing the DeepTwist
  framework to share weights across BERT models fine-tuned for different tasks.
  \item Our work demonstrates most weights need not change in the fine-tuning
  process.
%   \item This document describes the expected style, structure, and rough
%   proportions for your final project write-up.
%   \item While you are free to break from this structure, consider it a strong
%   prior for our expectations of the final report.
%   \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
%   in this format. While you can include supplementary material, it will not be
%   factored into the grading process. It is your responsibility to convey the
%   main contributions of the work in the length given.
  \end{itemize}
